%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

\include{template}


%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Zachary S. Hartwig, Ph.D.}
%\vspace{0.1cm}

%%
%% In modern CV's, it seems like ``Objective'' is frowned upon. Instead,
%% incorporate it into a well-constructed cover letter. The ``More
%% information'' can go at the end of the CV, but it should not distract
%% from the section giving references available to contact.
%%
%
% \section{Objective}
%
% Placement in an academic position (i.e., faculty, postdoctoral, or
% research scientist) that allows for advanced research in distributed
% complex adaptive systems (i.e., modeling, analysis, design, and
% verification) with a particular focus on the control of engineered
% agents (e.g., for communications, control, software, electronics, and
% sustainability) and the analysis of biological phenomena (e.g.,
% self-organization, ecological rationality)
% \begin{innerlist}
% \item More information and auxiliary documents can be found at\\\url{http://www.tedpavlic.com/facjobsearch/}
% \end{innerlist}

% \section{Research Interests}
% \textbf{Applying radiation detection and particle transport simulation
%   towards solving complex problems in nuclear science and
%   engineering}: nuclear diagnostics for plasma-wall interactions in
% magnetic fusion devices; digital data acquisition and pulse
% processing; advanced particle detectors for special nuclear material
% security; computational ion beam analysis for materials science; Monte
% Carlo particle transport development and simulation; compact
% superconducting cyclotrons for nuclear medicine and security;
% production of fundamental nuclear data; conceptual engineering designs
% of magnetic fusion devices.

\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\newcommand\spacechar{$|$}

\section{Research Interests}
\textbf{Advancing radiation detection, particle transport simulations,
  and ion beam analysis \\ to solve complex problems in nuclear
  science and engineering}\vspace{0.1cm}

\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\begin{innerlist}
\item Plasma-material interactions in magnetic fusion
\item Particle and radiation detectors
\item Monte Carlo particle transport simulation
\item Ion beam materials analysis
\end{innerlist}
}
% Shorten by removing \spacechar's
& \parbox{\spacewidth}{\centering} &

% Non-snail-mail contact information
\parbox{\rcollength}{%

\begin{innerlist}
\item Digital data acquisition and pulse processing
\item Production of fundamental nuclear data
\item Conceptual designs for magnetic fusion energy
\item Radiation detection for nuclear security
\end{innerlist}
}
\end{tabular}

\vspace{0.4cm}

\section{Education}

%\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
%\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
%\newcommand\spacechar{$|$}
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\textbf{Ph.D. in Nuclear Science}, MIT. February 2014.

\begin{innerlist}
\item Concentration: Fusion nuclear science
\item GPA: 4.7 / 5.0
\item Thesis: \emph{An accelerator-based in-situ diagnostic for plasma-material interactions science on magnetic fusion devices}
\end{innerlist}

}
% Shorten by removing \spacechar's
& \parbox{\spacewidth}{\centering} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\textbf{B.A. in Physics}, Boston University. May 2005.
\begin{innerlist}
\item Concentration: Experimental particle physics
\item GPA: 3.7 / 4.0
\item Degree awarded \emph{summa cum laude}
\item Recipient of Alumni Award in Physics
\item Dean's List all 8 semesters
\end{innerlist}
}
\end{tabular}

\vspace{0.4cm}

\section{Notable Achievements}
\begin{innerlist}
\item \textit{Recipient}, MIT NSE Del Favero Prize in Nuclear Science and Engineering, May 2014.
\item \textit{Fellow}, 2013 Kavli Frontiers of Science.
\item \textit{Invited talk}, Kavli Frontiers of Science Meeting, November, 2013.
\item \textit{Invited talk}, APS Division of Plasma Physics Meeting, Novermber, 2013.
\item \textit{USA Cycling National Champion}, Collegiate Track Division II Team Omnium. September 2012.
\item \textit{Recipient}, MIT NSE Special Award, Excellence in Science Communication and Policy. May 2012.
\item \textit{Recipient}, MIT Plasma Science and Fusion Center Award, Science Education and Outreach. July 2012.
\item \textit{Recipient}, MIT International Science and Technology Initative Global Seed Fund Grant. May 2011.
\item \textit{Keynote speaker}, MIT Nuclear Science and Engineering Department (NSE) Research Expo. March 2011.
\item \textit{Recipient}, Boston University Alumni Prize for Excellence in Physics. May 2005.
\end{innerlist}

\section{Research Experience}
\begin{innerlist}
\item \textbf{Postdoctoral Associate, MIT (2013-present)}: Continuing
  to develop ion beam analysis techniques and a novel
  accelerator-based diagnostic for plasma-material interactions in the
  Alcator C-Mod tokamak. Additionally participating in a new proposal
  for a synchrotron-based facility at Brookhaven to study materials
  under extreme irradiation.\vspace{0.2cm}

\item \textbf{Consultant, Tokamak Solution U.K. (2013-present)}:
  Advising a private company on Monte Carlo neutronics simulations for
  magnetic fusion applications. The work involves interacting with
  team members to improve existing simulations and developing
  high-fidelity plasma neutron source models.\vspace{0.2cm}

\item \textbf{Ph.D student, MIT (2007-2013)}: Designed and
  demonstrated an innovative accelerator-based materials diagnostic
  for magnetic fusion devices. The research involved creating advanced
  particle transport simulations, applying radiation detection in a
  challenging environment, implementing a custom digital data
  acquisition system, and creating analysis tools for digital pulse
  processing of detector data. Project involved significant team work
  with Alcator C-Mod personnel and mentoring of younger
  students.\vspace{0.2cm}

\item \textbf{Consultant, Neotron Inc. (2009-2010)}: Played a key role
  in the development of an innovative lithium-6-based detector for
  homeland security. The research involved creating high-fidelity
  models of proposed detector designs using particle transport
  simulations and working with a team to optimize cost and detection
  efficiency within the engineering constraints to achieve a final
  design.\vspace{0.2cm}
  
\item \textbf{Consultant, Cyclotron Group, MIT (2010)}: Predicted the
  deleterious effects of losing control of an accelerated particle
  beam in a proposed ultracompact superconducting cyclotron
  facility. The research involved creating and benchmarking a
  high-fidelity model of the cyclotron and calculating nuclear heating
  and radiation damage to the superconducting magnets as a result of
  various accident scenarios.\vspace{0.2cm}

\item \textbf{Research Assistant, Boston University (2004-2006)}:
  Developed a particle physics simulation for the Muon g-2 Experiment,
  which searches for physics beyond the Standard Model of particle
  physics. The simulation is presently used and developed by a
  world-wide collaboration as the leading computational design tool
  for the next generation of the experiment that will run at Fermilab
  National Accelerator Laboratory in 2016. Experimental work on
  particle detection and data acquisition performed on the M$\mu$LAN
  experiment to measure the lifetime of the muon at Paul Sherrer
  Institute, Switzerland, 2005.
\end{innerlist}

\newpage
\makeheading{Zachary S. Hartwig, Ph.D.}

\section{Teaching Experience}
\begin{innerlist}
\item \textbf{UROP advisor}: Florent Sainct (2009), Jake Jurewicz (2011), Gabriel Ledoux (2012, 2013)
\item \textbf{Undergraduate thesis mentor}: Lauren Chilton, MIT Class of 2012.
\item \textbf{Teaching assistant}: 22.63: Engineering Principles for Fusion Reactors (Prof. D. Whyte). Spring 2012.
\item \textbf{Teaching assistant}: 22.105 : Electromagnetic Interactions (Prof. D. Whyte). Fall 2010.
\item \textbf{Private tutor}: High school physics for several Boston University Academy Students. 2005-2006. 
\end{innerlist}

\section{Leadership Experience}
\begin{innerlist}
\item \textbf{Organizer}: U.S. fusion student advocacy trip to 30 Congressional offices in Washington DC. June 2012.
\item \textbf{Mediator}: Conflict resolution, MIT Resistance for Easing Friction and Stress Program. January 2010.
\end{innerlist}

\section{Hardware Expertise}
\textbf{Detector Data Acquisition}
\begin{innerlist}
  \item CAEN S.p.A. data acquisition systems, Tektronix digital oscilloscopes
\end{innerlist}

\halfblankline

\textbf{Particle Detector Construction}
\begin{innerlist}
\item Scintillator crystals, photomultiplier tubes, silicon avalanche
  photodiodes, silicon photomultiplier, signal preamplifiers,
  soldering, basic machining, detector test platforms
\end{innerlist}

\section{Computer expertise}

\textbf{Programming Languages}
\begin{innerlist}
  \item C, C$+$$+$, Java, Python, Unix shell scripting, GNU make, Matlab, IDL, Open MPI, MPICH2
\end{innerlist}

\halfblankline

\textbf{Particle Transport and Nuclear Physics Codes}
\begin{innerlist}
  \item Geant4, MCNP5/X, DAGMC CAD-based neutronics, SRIM/TRIM, EASY, NJOY, TALYS, EMPIRE
\end{innerlist}

\halfblankline

\textbf{Data acquisition, storage and analysis}
\begin{innerlist}
  \item ROOT, MDSplus
\end{innerlist}

\halfblankline

\textbf{Computer-Aided Design (CAD) and Analysis}
\begin{innerlist}
  \item Solid Edge ST5, CUBIT Tool Suite, COMSOL Multiphysics 4
\end{innerlist}

\halfblankline

\textbf{Productivity Software}
\begin{innerlist}
  \item Windows OS, Linux OS (Fedora, RHEL, Ubuntu), Emacs,
    Subversion, Git, GitHub, \LaTeX, LibreOffice, GIMP, Inkscape
\end{innerlist} 


% \section{Academic Coursework (MIT)}

% \newlength{\rcollengthtwo}\setlength{\rcollengthtwo}{3.1in}%

% \begin{tabular}[t]{@{}p{\textwidth-\rcollengthtwo-\spacewidth}@{}p{\spacewidth}@{}p{\rcollengthtwo}}%

% % Address box
% \parbox{\textwidth-\rcollengthtwo-\spacewidth}{%
%   \begin{innerlist}
%   \item   3.320 Atomistic Computer Materials Modeling
%   \item  18.085 Computational Science and Engineering
%   \item  22.071 Electronics, Signals, and Measurement
%   \item  22.101 Applied Nuclear Physics
%   \item  22.105 Electromagnetic Interactions
%   \item  22.106 Neutron Interactions and Applications
%   \item  22.51 Quantum Theory of Radiation Interactions
%   \item  22.611 Introduction to Plasmas Physics I
%   \end{innerlist}
% }

% & \parbox{\spacewidth}{\centering} &

% % Non-snail-mail contact information
% \parbox{\rcollengthtwo}{%

% \begin{innerlist}
% \item  22.612 Introduction to Plasmas Physics II
% \item  22.62 Fusion Energy
% \item  22.63 Engineering Principles of Fusion Reactors
% \item  22.70 Materials for Nuclear Applications
% \item  22.811 Sustainable Energy
% \item  22.814 Nuclear Non-Proliferation
% \item  22.93 Teaching Experience in Nuclear Science
% \end{innerlist}
% }

% \end{tabular}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------%
% The following is copyright and licensing information for
% redistribution of this LaTeX source code; it also includes a liability
% statement. If this source code is not being redistributed to others,
% it may be omitted. It has no effect on the function of the above code.
%----------------------------------------------------------------------%
% Copyright (c) 2007, 2008, 2009, 2010, 2011 by Theodore P. Pavlic
%
% Unless otherwise expressly stated, this work is licensed under the
% Creative Commons Attribution-Noncommercial 3.0 United States License. To
% view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc/3.0/us/ or send a letter to
% Creative Commons, 171 Second Street, Suite 300, San Francisco,
% California, 94105, USA.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
% MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
% IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
% CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
% TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
% SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
%----------------------------------------------------------------------%
