%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

\include{template}


%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Zachary S. Hartwig, Ph.D.}
%\vspace{0.1cm}

%%
%% In modern CV's, it seems like ``Objective'' is frowned upon. Instead,
%% incorporate it into a well-constructed cover letter. The ``More
%% information'' can go at the end of the CV, but it should not distract
%% from the section giving references available to contact.
%%
%
% \section{Objective}
%
% Placement in an academic position (i.e., faculty, postdoctoral, or
% research scientist) that allows for advanced research in distributed
% complex adaptive systems (i.e., modeling, analysis, design, and
% verification) with a particular focus on the control of engineered
% agents (e.g., for communications, control, software, electronics, and
% sustainability) and the analysis of biological phenomena (e.g.,
% self-organization, ecological rationality)
% \begin{innerlist}
% \item More information and auxiliary documents can be found at\\\url{http://www.tedpavlic.com/facjobsearch/}
% \end{innerlist}

% \section{Research Interests}
% \textbf{Applying radiation detection and particle transport simulation
%   towards solving complex problems in nuclear science and
%   engineering}: nuclear diagnostics for plasma-wall interactions in
% magnetic fusion devices; digital data acquisition and pulse
% processing; advanced particle detectors for special nuclear material
% security; computational ion beam analysis for materials science; Monte
% Carlo particle transport development and simulation; compact
% superconducting cyclotrons for nuclear medicine and security;
% production of fundamental nuclear data; conceptual engineering designs
% of magnetic fusion devices.

\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\newcommand\spacechar{$|$}

\section{Research Interests}
\textbf{The application of high-field superconducting magnets,
  materials science, and computational design to accelerate the
  demonstration and deployment of commercial fusion energy
  system \vspace{0.1cm}}\\
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
  \begin{innerlist}
  \item Superconducting fusion magnet engineering
  \item Fusion energy nuclear science and device design
  \item Radiation damage in fusion materials
  \item Fusion neutronics; Monte Carlo particle transport
\end{innerlist}
}
% Shorten by removing \spacechar's
& \parbox{\spacewidth}{\centering} &

% Non-snail-mail contact information
\parbox{\rcollength}{%

\begin{innerlist}
\item Digital data acquisition and analysis systems
\item Accelerator-based nuclear and material science
\item Radiation and particle detector development
\item Fusion plasma-material interaction science
\end{innerlist}
}
\end{tabular}

\vspace{0.4cm}

\section{Education}

%\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
%\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
%\newcommand\spacechar{$|$}
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\textbf{Ph.D. in Nuclear Science}, MIT. February 2014.

\begin{innerlist}
\item Concentration: Fusion nuclear science
\item GPA: 4.7 / 5.0
\item Thesis: \emph{An accelerator-based in-situ diagnostic for plasma-material interactions science on magnetic fusion devices}
\end{innerlist}

}
% Shorten by removing \spacechar's
& \parbox{\spacewidth}{\centering} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\textbf{B.A. in Physics}, Boston University. May 2005.
\begin{innerlist}
\item Concentration: Experimental particle physics
\item GPA: 3.7 / 4.0
\item Degree awarded \emph{summa cum laude}
\item Recipient of Alumni Award in Physics
\item Dean's List all 8 semesters
\end{innerlist}
}
\end{tabular}

\vspace{0.4cm}

\section{Notable Achievements}
\begin{innerlist}
\item \textit{Recipient}, U.S. Department of Energy ORISE Postdoctoral Fellowship, Jan 2015.
\item \textit{Recipient}, MIT NSE Del Favero Prize in Nuclear Science and Engineering, May 2014.
\item \textit{Fellow}, 2013 Kavli Frontiers of Science.
\item \textit{Invited speaker}, Kavli Frontiers of Science Meeting, November, 2013.
\item \textit{USA Cycling National Champion}, Collegiate Track Division II Team Omnium. September 2012.
\item \textit{Recipient}, MIT NSE Special Award, Excellence in Science Communication and Policy. May 2012.
\item \textit{Recipient}, MIT Plasma Science and Fusion Center Award, Science Education and Outreach. July 2012.
\item \textit{Recipient}, MIT International Science and Technology Initative Global Seed Fund Grant. May 2011.
\item \textit{Recipient}, Boston University Alumni Prize for Excellence in Physics. May 2005.
\end{innerlist}

\section{Research Experience}
\begin{innerlist}
\item \textbf{Assistant professor, MIT NSE (2017-present)}:
  Sucessfully advanced and launched the SPARC project. Co-founded
  Commonwealth Fusion Systems, a spin-out company pursing
  commercialization of fusion energy. Co-leading the SPARC Project at
  MIT and overseeing several key engineering design projects including
  development of high-current high-temperature superconducting cables
  and fusion neutronics design analysis. Continuing to lead the Vault
  Laboratory, a facility for accelerator-based fusion nuclear science
  including radiation damage in HTS and structural materials. Teaching
  responsibilities have include 22.011 (NSE freshmen seminar), 22.033
  (NSE senior design course), and 22.814 (Nuclear
  non-proliferation). Responsible for developing 22.061 (a new
  undergraduate fusion energy course).\vspace{0.2cm}
  
\item \textbf{Postdoctoral associate/fellow, MIT (2013-2016)}:
  Lead data acquisition, analysis, and computation efforts for two
  nuclear security projects (Low-dose monoenergetic gamma radiography
  system; Zero knowledge warhead verification system). Conducted
  on-going efforts to bring an ultracompact superconducting cyclotron
  to MIT for nuclear security and materials research. Proposed and
  lead a collaboration with MIT Aeronautics and Astronautics
  Engineering department on novel low-cost satellite-based particle
  spectrometers and dosimeters. Established a new accelerator science
  and detector development laboratory with collaborators.  Continued
  development of the AIMS diagnostic for plasma-material interaction
  science on the Alcator C-Mod tokamak.\vspace{0.2cm}

\item \textbf{Ph.D student, MIT (2007-2013)}: Designed and
  demonstrated an innovative accelerator-based materials diagnostic
  for magnetic fusion devices. The research involved creating advanced
  particle transport simulations, applying radiation detection in a
  challenging environment, implementing a custom digital data
  acquisition system, and creating data analysis tools.\vspace{0.2cm}

\item \textbf{Advisor, Neotron Inc. (2009-2010)}: Collaborated on
  development of an innovative lithium-6-based detector for homeland
  security. The research involved using particle transport simulations
  to optimize the design and cost of the final detector.\vspace{0.2cm}

\item \textbf{Research Assistant, Boston University (2004-2006)}:
  Developed a particle physics simulation for the Muon g-2 Experiment
  (Brookhaven and Fermi National Labs).  The simulation is presently
  used as a leading computational design tool for the next generation
  of the experiment. Performed experimental work on particle detection
  and data acquisition for the M$\mu$LAN muon lifetime experiment at
  Paul Sherrer Institute, Switzerland, 2005.
\end{innerlist}

\newpage
\makeheading{Zachary S. Hartwig, Ph.D.}

\section{Doctoral Dissertation}
\textbf{MIT Department of Nuclear Science and Engineering Ph.D. Dissertation}
\begin{innerlist}
\item Z.S. Hartwig (2013). \textit{An In-situ Accelerator-based Diagnostic
  for Plasma-Material Interactions on Magnetic Fusion Devices.}
Doctoral Dissertation, MIT, Cambridge MA,
USA.\\ \href{http://www.psfc.mit.edu/library1/catalog/reports/2010/13rr/13rr012/13rr012_full.pdf}{Available
  for download here}
\end{innerlist}

\section{Research Publications}
\textbf{Accelerator-based In-situ Materials Surveillance (AIMS)}
\begin{innerlist}

\item Z.S. Hartwig \textit{et al.} \textit{Fuel retention measurements
  in Alcator C-Mod using Accelerator-based In situ Materials
  Surveillance.} J. Nucl. Mat. \textbf{263} (2015) 73.
  \href{http://dx.doi.org/10.1016/j.jnucmat.2014.09.056}{doi:10.1016/j.jnucmat.2014.09.056}
  \vspace{0.2cm}

\item Z.S. Hartwig \textit{et al.} \textit{An in-situ
  accelerator-based diagnostic for plasma-material interactions on
  magnetic fusion devices.} Rev. Sci. Instr. \textbf{84} (2013)
  123503.
  \href{http://dx.doi.org/10.1063/1.4832420}{doi:10.1064/1.4832420}
  \vspace{0.2cm}

\item Z.S. Hartwig and D.G. Whyte. \textit{Simulated plasma-facing
  component measurements for an in-situ surface diagnostic on Alcator
  C-Mod.} Rev. Sci. Instr. \textbf{81} (2010)
  10E106.
  \href{http://dx.doi.org/10.1063/1.3478634}{doi:10.1063/1.4832420}
\end{innerlist}

\vspace{0.5cm}

\textbf{Magnetic fusion energy design and engineering}
\begin{innerlist}
\item Z.S. Hartwig \textit{et al.} \textit{An initial study of
  demountable, high-temperature superconducting magnets for the Vulcan
  tokamak conceptual design.} Fus. Eng. Design \textbf{87} (2012) 201.
  \\\href{http://dx.doi.org/10.1016/j.fusengdes.2011.10.002}{doi:10.1016/j.fusengdes.2011.10.002}
  \vspace{0.2cm}

\item G.M. Olynyk, Z.S. Hartwig, \textit{et al.} \textit{Vulcan: a
  steady-state tokamak for reactor-relevant plasma-material
  interaction science.} Fus. Eng. Design \textbf{87} (2012) 224.
  \href{http://dx.doi.org/10.1016/j.fusengdes.2011.12.009}{doi:10.1016/j.fusengdes.2011.12.009}
  \vspace{0.2cm}

\item G.M. Olynyk, Z.S. Hartwig, \textit{et al.} \textit{Assessing the
  feasibility of a high-temperature, helium-cooled vacuum vessel and
  first wall for the Vulcan tokamak conceptual design.} Fus. Eng. Design \textbf{87} (2012) 248.
  \href{http://dx.doi.org/10.1016/j.fusengdes.2011.12.018}{doi:10.1016/j.fusengdes.2011.12.018}
  \vspace{0.2cm}

\item D.G. Whyte \textit{et al.} \textit{Reactor similarity for
  plasma--material interactions in scaled-down tokamaks as the basis
  for the Vulcan conceptual design.} Fus. Eng. Design \textbf{87} (2012) 234.
  \href{http://dx.doi.org/10.1016/j.fusengdes.2011.12.011}{doi:10.1016/j.fusengdes.2011.12.011}\vspace{0.2cm}

\item Z.S. Hartwig and M. Zucchetti. \textit{Neutronics studies for a
  compact, high-field tokamak neutron source.}
  Fus. Sci. Tech. \textbf{60} (2011)
  725. \href{http://www.ans.org/pubs/journals/fst/a_12471}{Available online at http://www.ans.org/pubs/journals/fst/a\_12471}
\end{innerlist}

\vspace{0.5cm}

\textbf{Particle and radiation detector design, simulation, and data acquisition}
\begin{innerlist}
\item Z.S. Hartwig. \textit{The ADAQ framework: An integrated toolkit
  for data acquisition and analysis with real and simulated radiation
  detectors.} Nucl. Instr. and Meth. A \textit{In Press}, 2016.
  \href{http://dx.doi.org/10.1016/j.nima.2016.01.017}{doi:10.1016/j.nima.2016.01.017}\vspace{0.2cm}
  
\item Z.S. Hartwig and P. Gumplinger. \textit{Simulating response functions
  and pulse shape discrimination for organic scintillation detectors
  with Geant4}. Nucl. Instr. and Meth. A \textbf{737} (2014) 155.\\
  \href{http://dx.doi.org/10.1016/j.nima.2013.11.027}{doi:10.1016/j.nima.2013.11.027}
  \vspace{0.2cm}

\item A. Inglis \textit{et al.} \textit{Glass panel Lithium-6 Detector.}
IEEE Conference on Homeland Security (2012).\\
\href{http://dx.doi.org/10.1109/THS.2012.6459887}{doi:10.1109/THS.2012.6459887}
\end{innerlist}

\vspace{0.5cm}

\textbf{Experimental particle physics (The Muon Lifetime Analysis (M$\mu$LAN) experiment)}
\begin{innerlist}
\item  D.M. Webber \textit{et al.} \textit{Measurement of the positive muon
  lifetime and determination of the Fermi constant to
  part-per-million precision.} Phys. Rev. Lett. \textbf{106} (2011)
  041803.
  \href{http://dx.doi.org/10.1103/PhysRevLett.106.041803}{doi:10.1103/PhysRevLett.106.041803}\vspace{0.2cm}

\item V. Tishchenko \textit{et al.} \textit{Detailed report of the
  MuLan measurement of the positive muon lifetime and determination of
  the Fermi constant.} Phys. Rev. D. \textbf{87} (2013)
    052003. 
    \href{http://dx.doi.org/10.1103/PhysRevD.87.052003}{doi:10.1103/PhysRevD.87.052003}
\end{innerlist}

\section{Reference Publications}
\textbf{A comprehensive physics and mathematics reference for magnetic fusion}
\begin{innerlist}
\item Z.S. Hartwig and Y.A. Podpaly. \textit{The Magnetic Fusion
  Energy Formulary}. Self-published, 2016.
  \href{http://www-internal.psfc.mit.edu/research/MFEFormulary}{Available
    online at http://www-internal.psfc.mit.edu/research/MFEFormulary}.
\end{innerlist}

\newpage
\makeheading{Zachary S. Hartwig, Ph.D.}

\section{Teaching Experience}
\begin{innerlist}
\item \textbf{Lead instructor}: MIT 22.033 - NSE senior design course
\item \textbf{Lead instructor}: MIT 22.011 - NSE freshmen seminar course
\item \textbf{Co-instructor}: MIT 22.814 - NSE nuclear non-proliferation course
\item \textbf{Teaching assistant}: MIT 22.15 Essential Numerical Methods (Prof. I. Hutchinson). Fall 2013.
\item \textbf{Teaching assistant}: MIT 22.63 Engineering Principles for Fusion Reactors (Prof. D. Whyte). Spring 2012.
\item \textbf{Teaching assistant}: MIT 22.105 : Electromagnetic Interactions (Prof. D. Whyte). Fall 2010.
\item \textbf{UROP advisor}: Supervised over 10 UROPs during time at MIT
\item \textbf{Undergraduate thesis mentor}: Lauren Chilton (2012), Monica Phama (2018), Nick Schwartz (2018)
\item \textbf{Private tutor}: High school physics for several Boston University Academy Students. 2005-2006. 
\end{innerlist}

\section{Leadership Experience}
\begin{innerlist}
\item \textbf{Organizer}: U.S. fusion student advocacy trip to 30 Congressional offices in Washington DC. June 2012.
\item \textbf{Mediator}: Conflict resolution, MIT Resistance for Easing Friction and Stress Program. January 2010.
\end{innerlist}

\section{Hardware Expertise}
\textbf{Data Acquisition}
\begin{innerlist}
\item CAEN S.p.A. high-performance detector data acquisition systems
\item Raspberry Pi / Pi-plates data acquisition systems
\item Tektronix digital oscilloscopes and signal generators
\end{innerlist}

\halfblankline

\textbf{Particle Detector Construction}
\begin{innerlist}
\item Scintillator crystals, photomultiplier tubes, silicon avalanche
  photodiodes, silicon photomultiplier, signal preamplifiers,
  microcontrollers, soldering, basic machining, vacuum hardware,
  detector test platforms
\end{innerlist}

\section{Computer expertise}

\textbf{Programming Languages}
\begin{innerlist}
  \item C, C$+$$+$, Python, IPython/IPython notebooks, Open MPI, Unix shell scripting, GNU make, Matlab, IDL, HTML
\end{innerlist}

\halfblankline

\textbf{Particle Transport and Nuclear Physics Codes}
\begin{innerlist}
  \item Geant4, MCNP6/5/X, DAGMC CAD-based neutronics, SRIM/TRIM, EASY, NJOY, TALYS, EMPIRE
\end{innerlist}

\halfblankline

\textbf{Data acquisition, storage and analysis}
\begin{innerlist}
  \item ROOT, MDSplus
  \item Lead developer of the ADAQ framework
\end{innerlist}

\halfblankline

\textbf{Computer-Aided Design (CAD) and Analysis}
\begin{innerlist}
  \item Solid Edge ST5, CUBIT Tool Suite, COMSOL Multiphysics
\end{innerlist}

\halfblankline

\textbf{Cloud Computing}
\begin{innerlist}
  \item Amazon Web Services (EC2 Cloud Compute Framework)
\end{innerlist}

\halfblankline

\textbf{Productivity Software}
\begin{innerlist}
  \item Windows OS, Linux OS (Fedora, RHEL, Ubuntu), Emacs,
    Subversion, Git, GitHub, \LaTeX, GIMP, Inkscape
\end{innerlist} 

% \section{Academic Coursework (MIT)}

% \newlength{\rcollengthtwo}\setlength{\rcollengthtwo}{3.1in}%

% \begin{tabular}[t]{@{}p{\textwidth-\rcollengthtwo-\spacewidth}@{}p{\spacewidth}@{}p{\rcollengthtwo}}%

% % Address box
% \parbox{\textwidth-\rcollengthtwo-\spacewidth}{%
%   \begin{innerlist}
%   \item   3.320 Atomistic Computer Materials Modeling
%   \item  18.085 Computational Science and Engineering
%   \item  22.071 Electronics, Signals, and Measurement
%   \item  22.101 Applied Nuclear Physics
%   \item  22.105 Electromagnetic Interactions
%   \item  22.106 Neutron Interactions and Applications
%   \item  22.51 Quantum Theory of Radiation Interactions
%   \item  22.611 Introduction to Plasmas Physics I
%   \end{innerlist}
% }

% & \parbox{\spacewidth}{\centering} &

% % Non-snail-mail contact information
% \parbox{\rcollengthtwo}{%

% \begin{innerlist}
% \item  22.612 Introduction to Plasmas Physics II
% \item  22.62 Fusion Energy
% \item  22.63 Engineering Principles of Fusion Reactors
% \item  22.70 Materials for Nuclear Applications
% \item  22.811 Sustainable Energy
% \item  22.814 Nuclear Non-Proliferation
% \item  22.93 Teaching Experience in Nuclear Science
% \end{innerlist}
% }

% \end{tabular}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------%
% The following is copyright and licensing information for
% redistribution of this LaTeX source code; it also includes a liability
% statement. If this source code is not being redistributed to others,
% it may be omitted. It has no effect on the function of the above code.
%----------------------------------------------------------------------%
% Copyright (c) 2007, 2008, 2009, 2010, 2011 by Theodore P. Pavlic
%
% Unless otherwise expressly stated, this work is licensed under the
% Creative Commons Attribution-Noncommercial 3.0 United States License. To
% view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc/3.0/us/ or send a letter to
% Creative Commons, 171 Second Street, Suite 300, San Francisco,
% California, 94105, USA.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
% MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
% IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
% CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
% TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
% SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
%----------------------------------------------------------------------%
